---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# zarrr

<!-- badges: start -->
<!-- badges: end -->

The goal of zarrr is to ... learn xarray and python and read Zarr in R. 

WIP


## Example

This reads a slice from a zarr file via xarray, orients from xarray/numpy to R and plots with an extent (using raster/GDAL data orientation assumption). 

Example and inspiration take from this really excellent aggregation example by Ryan Abernathy. I'm using this to demonstrate a similar approach in R, for me to learn python and explore ideas. 

https://discourse.pangeo.io/t/conservative-region-aggregation-with-xarray-geopandas-and-sparse/2715

To open the Zarr source do 

```{r xarray_zarr}
library(zarrr)
store <- "https://ncsa.osn.xsede.org/Pangeo/pangeo-forge/gpcp-feedstock/gpcp.zarr"
z <- xarray_zarr(store)
```

We can now use the xarray facilities. 

```{r xarray}
## get coordinate bounds and a data slice
xc <- z$lon_bounds$values
yc <- z$lat_bounds$values

library(reticulate)  ## for dict()
shape <- z$precip$shape
#
precip0 <- z$precip$isel(dict(time = 0L))$values
precipn <- z$precip$isel(dict(time = as.integer(shape[[1]] - 1)))$values
library(ximage)
ex <- c(range(xc), range(yc))  ## these are regular grid
par(mfrow  = c(2, 1), mar = rep(0, 4))
cols <- hcl.colors(128)
zlim <- z$precip$valid_range
ximage(precip0, col = cols, zlim = zlim, asp = 1, extent = ex); maps::map('world2', add = TRUE, col = "white")
ximage(precipn, col = cols, zlim = zlim, asp = 1, extent = ex); maps::map('world2', add = TRUE, col = "white")

```

In zarrr we have a global 'xarray' object, that is equivalent to 'xr' in `python import xarray as xr`. 'xarray_zarr()' in this
package is just a helper for the following python-equiv code. 

```{r example}
library(zarrr)
store <- "https://ncsa.osn.xsede.org/Pangeo/pangeo-forge/gpcp-feedstock/gpcp.zarr"
zarrr:::xarray$open_dataset(store, engine = 'zarr', chunks = dict())
```

---

## Code of Conduct
  
Please note that the zarrr project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
