---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# zarrr

<!-- badges: start -->
<!-- badges: end -->

The goal of zarrr is to ... learn xarray and python and read Zarr in R. 

WIP


## Example

This reads a slice from a zarr file via xarray, orients from xarray/numpy to R and plots with an extent (using raster/GDAL data orientation assumption). 

All hardcoded for now, use `read_zarr()` to read a slice from the 3rd dim - use `read_zarr_raw()` to get an entire array by name. 

Example and inspiration take from this really excellent aggregation example by Ryan Abernathy. I'm using this to demonstrate a similar approach in R, for me to learn python and explore ideas. 

https://discourse.pangeo.io/t/conservative-region-aggregation-with-xarray-geopandas-and-sparse/2715


```{r example}
source("read_zarr.R", echo = TRUE)
```
